Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-03-07 meta_analysis_sexual_selection_pop_fitness.Rmd
7/3 Update

#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci), height = 0.1) +
  geom_point(size = 1.5) +
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes.

###Quantitative Summary Mean

@@

>Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom)

@@

>>>>

#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci), height = 0.1) +
  geom_point(size = 1.5) +
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

###Quantitative summary using bootstrapped means

@@

>Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom), or done for each outcome?

@@

**Comparisons of Stress vs Unstresss through anovas**
